SubsidyExplorer - Step 0: Data Wrangling

### 2020-03-13 scripts/01_data_wrangling.Rmd
moving all data and analysis over to this repo

```{r setup, include=FALSE}
library(knitr) 
library(countrycode) # country name matching
library(WDI) # World Bank GDP and population numbers by country
library(janitor) # cleaning column names
library(tidyverse)
library(readxl)
```

```{r}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

@@

results_dir <- here::here("results", "00-data-wrangling/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

# Introduction

This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer toolkit. It outputs tidyed data files to `r data_dir`.

It also creates and outputs four aggregated CSV files that are used as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`): 
- subsidies-2009-2018-tidy.csv
- demographic-2000-2018-tidy.csv
- fisheries-2000-2017.csv
- fao-landings-group-2000-2017.csv

Summary figures are exported to `r results_dir`.

@@

# Paths to misc data files 
costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
```

@@

# # Create variable for matching 
# oecd_matching <- oecd_lookup %>%
#   mutate(code_for_matching = case_when(!is.na(ssubtype_code) ~ ssubtype_code,
#                                        !is.na(subtype_code) ~ subtype_code,
#                                        !is.na(type_code) ~ type_code))

>>>>

```{r}
# Packages
library(knitr) 
library(countrycode) # country name matching
library(here)
library(WDI) # World Bank GDP and population numbers by country
library(janitor) # cleaning column names
library(tidyverse)
library(readxl)

# Code chunk defaults
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE, include = FALSE)

# Source helper file
source(here::here("scripts", "00_helpers.R"))

@@

results_dir <- here::here("results", "01-data-wrangling/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

# Description

This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer analysis. It outputs tidyed data files to `r data_dir`. Some of these tidied data files are used directly as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`).

@@

# Paths to fisheries mgmt files 
costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", )
ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
anderson_fpi_path <- here::here("data", "raw", "Anderson-et-al-")

# Paths to other files
iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
```

@@
